Multi-target detection with application to cryo-electron microscopy

### 2019-03-05 inverse_problems/inverse_problems.tex
sec 4 (first paragraph)

We begin this section by showing that in the homogeneous case ($K=1$) ,under both the well-separated and the Poisson models, the first three observed autocorrelations  identify the signal $x$, $\gamma$ and $\sigma^2$.  Then, we bound the maximal number of signals that can be recovered from those autocorrelations, and discuss multi-dimensional signals.

Before that, we start by showing that in the homogeneous case a signal $z\in\RL$ is identified uniquely by its second and the third autocorrelations.
 Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly using this identity for $k = 0, \ldots, L-1$:
%
\begin{equation}
%
z[k]  = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]}.
\label{eq-uniqueness}
%
\end{equation}
This proves the following useful fact:
\begin{proposition} \label{prop:uniqueness}
	%
	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$. 
\end{proposition}

Note that the procedure described in~\eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations. In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex LS procedure, which is empirically more robust to additive noise; we have observed similar phenomena for related problems~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
%
%In what follows, we show that in the homogeneous case $K=1$, the signal $x$, the parameter $\gamma$ and $\sigma^2$ are identified uniquely from the first three observed autocorrelations under both the well-separated and Poisson models. Then, we bound the maximal number of signals that can be recovered from  those autocorrelations in the heterogeneous case, and discuss extensions to multi-dimensional signals.

>>>>

We begin this section by showing that in the homogeneous case ($K=1$) ,under both the well-separated and the Poisson models, the first three observed autocorrelations  identify the signal $x$, $\gamma$ and $\sigma^2$.  Then, we bound from above the number of signals that can be recovered from those autocorrelations, and discuss multi-dimensional signals.

Before that, we start by showing that in the homogeneous case a signal $z\in\RL$ is identified uniquely by its second and the third autocorrelations.
 Indeed, assuming $z[0]$ and $z[L-1]$ are nonzero (otherwise, redefine the length of the signal), we can recover $z$ explicitly by 
\begin{equation}
%
z[k]  = \frac{z[0]z[k]z[L-1]}{z[0]z[L-1]} = \frac{a_z^3[k,L-1]}{a_z^2[L-1]},
\label{eq-uniqueness}
%
\end{equation}
for $k = 0, \ldots, L-1$.
This proves the following useful fact:
\begin{proposition} \label{prop:uniqueness}
	%
	A signal $z\in\RL$ is determined uniquely from  $a_z^2$ and $a_z^3$. 
\end{proposition}

Note that the procedure described in~\eqref{eq-uniqueness} is not numerically stable: if $z[0]$ or $z[L-1]$ are close to 0, recovery of $z$ is sensitive to errors in the autocorrelations. In practice, we recover $z$ by fitting it to its autocorrelations using a nonconvex LS procedure, which is empirically more robust to additive noise; we have observed similar phenomena for the related problem of multi-reference alignment~\cite{bendory2017bispectrum,boumal2017heterogeneous,abbe2017multireference}.
